\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-03-31 journalSwarmControl/Introduction.tex
The newest version of the TASE paper

%Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion.  
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Limited computation and communication rules out autonomous operation or direct control over individual units; instead we must rely on global control signals broadcast to the entire particle population.    
This paper examines object manipulation by a swarm of particles, each actuated by the same, shared global input, as illustrated in Fig.~{\ref{fig:bigPictureMeanAndVarianceForSwarm}.

@@

The goal was to test several scenarios involving large-scale human-swarm interaction (HSI), and to do so with a statistically-significant sample size. Towards this end, we created \href{http://www.swarmcontrol.net/show_results}{SwarmControl.net}, an open-source, online testing platform suitable for inexpensive deployment and data collection on a scale not yet seen in swarm robotics research. Screenshots from this platform are shown in Fig.~\ref{fig:5experiments}.  \href{https://github.com/crertel/swarmmanipulate.git}{All code} \href{http://www.swarmcontrol.net/show_results}{and experimental results} are online at \cite{Chris-Ertel2016}.

@@

%Inspired by our online experiments, because it is not always possible to gather pose information on each robot for feedback control and
%It is not always practical to gather pose information on individual robots for feedback control; the robots might be difficult or impossible to sense individually due to their size and location. However, it is often possible to sense global properties of the group, such as mean position and density.
Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group, such as mean position and variance. 
To make progress in automatic control with global inputs, this paper presents swarm manipulation controllers, inspired by our online experiments, that require only mean and variance measurements of the particle's positions.  
These controllers are used as primitives to perform the object manipulation task illustrated in Fig.~\ref{fig:bigPictureMeanAndVarianceForSwarm}.

>>>>

%Micro- and nanorobotics have the potential to revolutionize many applications including targeted material delivery, assembly, and surgery.  The same properties that promise breakthrough solutions---small size and large populations---present unique challenges to generating controlled motion.  
Large populations of micro- and nanorobots are being produced in laboratories around the world, with diverse potential applications in drug delivery and construction, see \cite{Peyer2013,Shirai2005,Chiang2011}. These activities require robots that behave intelligently.
Limited computation and communication rules out autonomous operation or direct control over individual units; instead we must rely on global control signals broadcast to the entire particle population.    
This paper examines object manipulation by a swarm of particles, each actuated by the same shared global input, as illustrated in Fig.~{\ref{fig:bigPictureMeanAndVarianceForSwarm}.

@@

The goal was to test several scenarios involving large-scale human-swarm interaction (HSI), and to do so with a statistically-significant sample size. Towards this end, we have created \href{http://www.swarmcontrol.net/show_results}{SwarmControl.net}: an open-source, online testing platform suitable for inexpensive deployment and data collection on a scale not yet seen in swarm robotics research. Screenshots from this platform are shown in Fig.~\ref{fig:5experiments}.  \href{https://github.com/crertel/swarmmanipulate.git}{All code} \href{http://www.swarmcontrol.net/show_results}{and experimental results} are online at \cite{Chris-Ertel2016}.

@@

%Inspired by our online experiments, because it is not always possible to gather pose information on each robot for feedback control and
%It is not always practical to gather pose information on individual robots for feedback control; the robots might be difficult or impossible to sense individually due to their size and location. However, it is often possible to sense global properties of the group, such as mean position and density.
Often particles are difficult or impossible to sense individually due to their size and location. 
For example, microrobots are smaller than the minimum resolution of a clinical MRI-scanner, see \cite{martel2014computer}, however it is often possible to sense global properties of the group such as mean position and variance. 
To make progress in automatic control with global inputs, this paper presents swarm manipulation controllers inspired by our online experiments that require only mean and variance measurements of the particle's positions.  
These controllers are used as primitives to perform the object manipulation task illustrated in Fig.~\ref{fig:bigPictureMeanAndVarianceForSwarm}.

### 2017-03-31 journalSwarmControl/expResults.tex
The newest version of the TASE paper

\paragraph{Varying number:}
\begin{figure}
\begin{overpic}[width = 0.9\columnwidth]{ResVaryNum.pdf}\end{overpic}
%\begin{overpic}[width = 0.48\columnwidth]{measureLearning.pdf}\end{overpic}
\caption{
\label{fig:ResVaryNu}Data from \emph{Varying Number} using particles to push an object through a maze to a goal location. 
% Best-fit linear and quadratic lines are overlaid for comparison. 
%(Right) Skill improves as players retry tests using data from \emph{Varying Number}.
}
\end{figure}

@@

\paragraph{Varying visualization:}
\begin{figure}[b!]
\renewcommand{\figwid}{0.24\columnwidth}
\begin{overpic}[width =\figwid]{VaryVisFS.pdf}\put(20,15){Full-state}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisCH.pdf}\put(10,15){Convex-hull}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}\put(10,15){Mean + var}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMe.pdf}\put(30,15){Mean}\end{overpic}
\vspace{-.5em}
\caption{\label{fig:Visualization}Screenshots from task \emph{Vary Visualization}. This experiment challenges players to quickly steer 100 particles (blue discs) to push an object (green hexagon) into a goal region. We record the completion time and other statistics.
%\vspace{-1em}
}
\end{figure}

@@

Our hypothesis predicted a steady decay in performance as the amount of visual feedback decreased.
Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [mean, mean + variance, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing. 
Using ANOVA analysis, we reject the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 particles is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers described convex-hull feedback as confusing and irritating.  A single particle left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

\paragraph{Varying noise:}
%Micro-particles are affected by random collisions with molecules. The effect of these collisions is called Brownian motion.
This experiment varied the strength of %these 
disturbances to study how noise affects human control of large swarms. Noise was applied at every timestep:
\begin{align*}
\dot{x}_i &= u_x + m_i\cos(\psi_i)\\
 \dot{y}_i &= u_y + m_i\sin(\psi_i).
 \end{align*}
$m_i,\psi_i$ were uniformly IID, with $m_i\in[0,M]$ and $\psi_i\in[0,2\pi]$. $M$ was a constant for each trial ranging from 0 to 200\% of the maximum control power ($u_{max}$).

@@

\paragraph{Position control:}
This online experiment examined how completion time scales with the number of particles $n$. Using a single square obstacle, users arranged $n\in[1,10]$ particles into a specified goal pattern.  The goal pattern formed a block  {\sffamily A} with 10 particles, and lesser numbers of particles used a subset of these goal positions. Our hypothesis was that completion time would increase linearly with the number of particles, as with our position control algorithm in \cite{Becker2013b}.  Our results roughly corroborate this, as shown in Fig.~\ref{fig:ResVaryNoisePosition}.b.  Though the number of particles presented to game players is uniformly distributed, larger $n$ are more difficult, and the number of successful experiments drops steadily as $n$ increases.

@@

\paragraph{Varying control--Assembly:}
Ultimately, we want to use swarms of particles to build things. This experiment compared different control architectures modeled after real-world devices.

@@

\paragraph{Varying control--Foraging:}
Collecting and delivering resources is necessary for drug delivery.
This experiment also compared attractive and repulsive control with the global control used for the other experiments. The experiment challenged players to collect particles using a swarm of 100 particles and return the particles to a home region. The particles encapsulate the particles on contact.

>>>>

\paragraph{Varying number}
\begin{figure}
\begin{overpic}[width = 0.9\columnwidth]{ResVaryNum.pdf}\end{overpic}
%\begin{overpic}[width = 0.48\columnwidth]{measureLearning.pdf}\end{overpic}
\caption{
\label{fig:ResVaryNu}Data from \emph{Varying Number} using particles to push an object through a maze to a goal location. 
% Best-fit linear and quadratic lines are overlaid for comparison. 
%(Right) Skill improves as players retry tests using data from \emph{Varying Number}.
}
\end{figure}

@@

\paragraph{Varying visualization}
\begin{figure}[b!]
\renewcommand{\figwid}{0.24\columnwidth}
\begin{overpic}[width =\figwid]{VaryVisFS.pdf}\put(20,15){Full-state}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisCH.pdf}\put(10,15){Convex-hull}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMV.pdf}\put(10,15){Mean + var}\end{overpic}
\begin{overpic}[width =\figwid]{VaryVisMe.pdf}\put(30,15){Mean}\end{overpic}
\vspace{-.5em}
\caption{\label{fig:Visualization}Screenshots from task \emph{Vary Visualization}. This experiment challenges players to quickly steer 100 particles (blue discs) to push an object (green hexagon) into a goal region. We record the completion time and other statistics.
%\vspace{-1em}
}
\end{figure}

@@

Our hypothesis predicted a steady decay in performance as the amount of visual feedback decreased.
Our experiment indicated the opposite: players with just the mean completed the task faster than those with full-state feedback.  As Fig.~\ref{fig:ResVaryVis}.b shows, the levels of feedback arranged by increasing completion time are [mean, mean + variance, full-state, convex-hull].  All experiments lasting over 300s were removed, under the assumption that the user stopped playing. 
Using ANOVA analysis, we rejected the null hypothesis that all visualization methods are equivalent, with $p$-value $2.69\times10^{-19}$.
Anecdotal evidence from beta-testers who played the game suggests that tracking 100 particles is overwhelming---similar to schooling phenomenons that confuse predators---while working with just the mean + variance is like using a ``spongy'' manipulator. Our beta-testers described convex-hull feedback as confusing and irritating.  A single particle left behind an obstacle will stretch the entire hull, obscuring the majority of the swarm.
%obscuring what the rest of the swarm is doing.

\paragraph{Varying noise}
%Micro-particles are affected by random collisions with molecules. The effect of these collisions is called Brownian motion.
This experiment varied the strength of %these 
disturbances to study how noise affects human control of large swarms. Noise was applied at every timestep:
\begin{align*}
\dot{x}_i &= u_x + m_i\cos(\psi_i)\\
 \dot{y}_i &= u_y + m_i\sin(\psi_i).
 \end{align*}
$m_i,\psi_i$ were uniformly IID, with $m_i\in[0,M]$ and $\psi_i\in[0,2\pi]$. $M$ was a constant for each trial ranging from 0 to 200\% of the maximum control power ($u_{max}$).

@@

\paragraph{Position control}
This online experiment examined how completion time scales with the number of particles $n$. Using a single square obstacle, users arranged $n\in[1,10]$ particles into a specified goal pattern.  The goal pattern formed a block  {\sffamily A} with 10 particles, and lesser numbers of particles used a subset of these goal positions. Our hypothesis was that completion time would increase linearly with the number of particles, as with our position control algorithm in \cite{Becker2013b}.  Our results roughly corroborate this, as shown in Fig.~\ref{fig:ResVaryNoisePosition}.b.  Though the number of particles presented to game players is uniformly distributed, larger $n$ are more difficult, and the number of successful experiments drops steadily as $n$ increases.

@@

\paragraph{Varying control--Assembly}
Ultimately, we want to use swarms of particles to build things. This experiment compared different control architectures modeled after real-world devices.

@@

\paragraph{Varying control--Foraging}
Collecting and delivering resources is necessary for drug delivery.
This experiment also compared attractive and repulsive control with the global control used for the other experiments. The experiment challenged players to collect particles using a swarm of 100 particles and return the particles to a home region. The particles encapsulate the particles on contact.

### 2017-03-31 journalSwarmControl/experiment.tex
The newest version of the TASE paper

This section analyzes an \emph{object manipulation} task attempted by our hybrid, hysteresis-based controllers, inspired by the analysis of human users in \S \ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task, we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

@@

To design the policy, we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$  shown in Fig.~\ref{fig:BFSGradient}.  
The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$, so we define the desired direction for the object as $\mathbf{D}(\mathbf{b}) = \nabla \mathbf{M}(\mathbf{b})$. 
The robots were directed behind the object at  $\mathbf{b} - 1.5 r_b \mathbf{D}(\mathbf{b})$, then directed to  $\mathbf{b} - 0.1 r_b \mathbf{D}(\mathbf{b})$ to push the object toward the goal location. 
This approach using workspace BFS fails to account for the hull of the object and will suggest moves that can cause collisions with the workspace. A configuration-space BFS approach avoids that problem but still fails to model uncertain actuation of the object by the swarm.

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{SimVeryNum.pdf}\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{SimVeryNoise.pdf}\put(1,55){b)}
\end{overpic}
\begin{overpic}[width =\figwid]{SimVeryWeight.pdf}\put(1,55){c)}
\end{overpic}
\begin{overpic}[width =\figwid]{SimVeryShape.pdf}\put(1,55){d)}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:AutoVeryParam}Parameter sweep for a) number of robots, b) different noise values, c) object weight, and d) object shape.  Each bar is labelled with the number of trials. Completion time is in seconds.
%\vspace{-2em}
}
\end{figure*}

>>>>

This section analyzes an \emph{object manipulation} task attempted by our hybrid, hysteresis-based controllers.%, inspired by the analysis of human users in \S \ref{sec:expResults}.  
The swarm must deliver the object to the goal region.  To solve this object manipulation task we divide the task into two components: designing a policy for the object, and designing a control law for the swarm to push the object according to the policy.

@@

To design the policy we first discretize the environment. 
In \cite{ShahrokhiIROS2015}, we used breadth-first search (BFS) on this discretized grid to determine $\mathbf{M}_{BFS}$, the shortest distance from any grid cell to the goal, and generated a gradient map $\nabla \mathbf{M}$  shown in Fig.~\ref{fig:BFSGradient}.  
The object's center of mass is at $\mathbf{b}$ and has average radius $r_b$, so we define the desired direction for the object as $\mathbf{D}(\mathbf{b}) = \nabla \mathbf{M}(\mathbf{b})$. 
The robots were directed behind the object at  $\mathbf{b} - 1.5 r_b \mathbf{D}(\mathbf{b})$, then directed to  $\mathbf{b} - 0.1 r_b \mathbf{D}(\mathbf{b})$ to push the object toward the goal location. 
This approach using workspace BFS fails to account for the hull of the object and will suggest moves that can cause collisions with the workspace. A configuration-space BFS approach avoids that problem but still fails to model uncertain actuation of the object by the swarm.

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.5\columnwidth}
\begin{overpic}[width =\figwid]{SimVeryNum.pdf}\put(1,55){a)}
\end{overpic}
\begin{overpic}[width =\figwid]{SimVeryNoise.pdf}\put(1,55){b)}
\end{overpic}
\begin{overpic}[width =\figwid]{SimVeryWeight.pdf}\put(1,55){c)}
\end{overpic}
\begin{overpic}[width =\figwid]{SimVeryShape.pdf}\put(1,55){d)}
\end{overpic}
\vspace{-0.5em}
\caption{\label{fig:AutoVeryParam}Parameter sweep simulation studies for a) number of robots, b) different noise values, c) object weight, and d) object shape.  Each bar is labelled with the number of trials. Completion time is in seconds.
%\vspace{-2em}
}
\end{figure*}

### 2017-03-31 journalSwarmControl/realExperiment.tex
changed order of video numbers
Added rectangle
The newest version of the TASE paper

The kilobots performed five successful runs of object manipulation through the obstacle maze.
Each trial used 100 kilobots. Videos of each are in the multimedia extension. Trials two-five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std). 
A circular object completed in 3155 s.    
A square object completed in 6871 s. 
Three equilateral triangular objects of varying sizes failed in a total of seven runs.  Failures occurred when the object was pushed into a corner, requiring torque to be unstuck.  This paper focuses on force, but not torque control. Swarm torque control is the subject of ongoing research in \cite{Shahrokhi2016CASE}.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(48,8){\emph{t} = 2185 s}\put(80,8){\emph{t} = 2703 s}
\end{overpic}
%\vspace{-1em}
\caption{\label{fig:expSnapShot}Snapshots showing object manipulation experiment with 100 kilobots under automatic control. The automatic controller generates a policy to the goal. See  supplementary material video 1.}
        \end{figure}

>>>>

The kilobots performed five successful runs manipulating a hexagonal object through an obstacle maze. Videos of these runs are in Extension 2.
Each trial used 100 kilobots. Trials two through five were performed in a row with no failures in between.  For each trial, fully charged kilobots were placed in the lower left-hand of the workspace, as shown in Fig.~\ref{fig:expSnapShot}.  The moveable object was placed in the lower center of the workspace.  {\sc Matlab} code for vision processing, the policy iteration of \S \ref{subsec:objectpolicy} and the algorithm of \S \ref{sec:AlgObjectManipulation} is available on {\sc Matlab} Central by \cite{Shahrokhi2015MDP}.
Trials were run until the object COM entered the goal region.  The trials ran for \{1465, 3457, 3000, 2162, 2707\} s.  This is $2558\pm771$ s (mean$\pm$std).

We also tested other object shapes. 
A circular object completed in 3155 s.    
A square object completed in 6871 s. 
A rectangle and three equilateral triangle objects of varying sizes failed in a total of nine runs. 
Manipulation failures occurred when the object was pushed into a corner, requiring torque to be unstuck.  
%This paper focuses on force, but not torque control. 
Swarm torque control is the subject of our ongoing research begun in \cite{Shahrokhi2016CASE}.

@@

\begin{figure}
\centering
%\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,29){\emph{t} = 3 s}\put(38,29){\emph{t} = 410 s}\put(70,29){\emph{t} = 710 s}
%\put(15,22){\emph{t} = 1374 s}\put(49,22){\emph{t} = 2185 s}\put(83,22){\emph{t} = 2703 s}
%\end{overpic}
\begin{overpic}[width=\columnwidth]{Snapshots.pdf}\put(6,80){\emph{t} = 3 s}\put(38,80){\emph{t} = 410 s}\put(70,80){\emph{t} = 710 s}
\put(15,8){\emph{t} = 1374 s}\put(48,8){\emph{t} = 2185 s}\put(80,8){\emph{t} = 2703 s}
\end{overpic}
%\vspace{-1em}
\caption{\label{fig:expSnapShot}Snapshots showing object manipulation experiment with 100 kilobots under automatic control. The automatic controller generates a policy to the goal, (see Extension 2).}
        \end{figure}

### 2017-03-31 journalSwarmControl/relatedWork.tex
The newest version of the TASE paper

\subsection{Global control of microrobots}
Small robots have been constructed with physical heterogeneity so that they respond differently to a global, broadcast control signal.  Examples include \emph{scratch-drive microrobots}, actuated and controlled by a DC voltage signal from a substrate by \cite{Donald2006,Donald2008};   magnetic structures  with different cross-sections that could be independently steered by \cite{Floyd2011,Diller2013};   \emph{MagMite} microrobots with different resonant frequencies and a global magnetic field by \cite{Frutiger2008}; and  magnetically controlled nanoscale helical screws constructed to stop movement at different cutoff frequencies of a global magnetic field by
\cite{Tottori2012} and \cite{Peyer2013}.

@@

  Most humans are able, with practice, steer a swarm of robots controlled by a global input. Prior to our paper, no algorithm existed. Using human input to learn how to control a dynamic system is a line of research with a rich history \cite{argall2009, abbeel2010}.This paper exploits insights gained from ``swarmcontrol.net", particularly the fact that having a swarm's mean and variance is sufficient for object manipulation through an obstacle field.

@@

Our $n$-robot system with 2 control inputs and 4$n$ states is inherently under-actuated, and superficially bears resemblance to compliant, under-actuated manipulators.  Our swarms conform to the object to be manipulated, but lack the restoring force provided by flexures in \cite{odhner2014compliant} or silicone in \cite{deimel2014novel}.  Our swarms tend to disperse, so we require  artificial forces, such as the variance control primitives in \S \ref{sec:VarianceControl},
 to regroup the swarms.

>>>>

\subsection{Global control of microrobots}
Small robots have been constructed with physical heterogeneity so that they respond differently to a global broadcast control signal.  Examples include \emph{scratch-drive microrobots}, actuated and controlled by a DC voltage signal from a substrate by \cite{Donald2006,Donald2008};   magnetic structures  with different cross-sections that can be independently steered by \cite{Floyd2011,Diller2013};   \emph{MagMite} microrobots with different resonant frequencies and a global magnetic field by \cite{Frutiger2008}; and  magnetically controlled nanoscale helical screws constructed to stop movement at different cutoff frequencies of a global magnetic field by
\cite{Tottori2012} and \cite{Peyer2013}.

@@

  Most humans are able to, with practice, steer a swarm of robots controlled by a global input. Prior to our paper, no algorithm existed. Using human input to learn how to control a dynamic system is a line of research with a rich history \cite{argall2009, abbeel2010}.This paper exploits insights gained from ``swarmcontrol.net", particularly the fact that having a swarm's mean and variance is sufficient for object manipulation through an obstacle field.

@@

Our $n$-robot system with 2 control inputs and 4$n$ states is inherently under-actuated, and superficially bears resemblance to compliant, under-actuated manipulators.  Our swarms conform to the object to be manipulated, but lack the restoring force provided by flexures in \cite{odhner2014compliant} or silicone in \cite{deimel2014novel}.  Our swarms tend to disperse and so to regroup them we require artificial forces like the variance control primitives in\S \ref{sec:VarianceControl}.
